### 2025-01-15 reviewer-response.md

*For example, line 215, does the cost of partitioning of O(n log(n)) depend on
the tree being balanced? It is an important hypothesis because line 197 states
that "the imbalance in the tree is a feature, not a bug, as it reflects the
underlying structure of the data". That may look like a contradiction.*

We have attempted to address this by including additional computational experiments: in section 4.?, we have included plots indicating performance where we forced a balanced tree (in general, this performs worse, as we expected). TODO Najib go over this paragraph.

*The cost on line 260 uses $\hat{r}$, which is a mean radius. Now that cost is in
expectation (in addition to the balanced tree hypothesis).*

This is restating the complexity from the CHESS paper, but it's correct that it's an expected cost. Worst-case analysis isn't really useful here.

@@

*Another example, line 326, comes from the minimum with value 2 on line 284. If
the assumption on the LFD is not satisfied, then an extra log factor would
appear in the cost.*

write in plain english right after eq 2.3, explaining in plain english the rationale for the min(2,x) expansion: namely, we don't think the very low LFD would be representative of what we'd see if we massively increased the radius (TODO Morgan)

*The discussion on LFD after its definition line 141 is hard to understand:
there are 2 parameters in the definition of LFD (r_1 and r_2), but the
discussion seems to imply there is only 1 (a radius r). That discussion only
seems to make sense after line 163 and the rewrite of the definition 2.1.*

We have revised the LFD definitions in this section for clarity.

@@

*Smith-Waterman and Needleman-Wunsch are not distances (unlike Levenshtein and
Hamming distances). They are dynamic programming algorithms to compute
distances like the Levenshtein distance (and others depending on the exact
parameters of the algorithms).*

This has been fixed.

*The explanation that the augmentation process (starting at line 418) preserves
the topological structure of the underlying data is not very convincing. This
process adds small clouds of points extending in every dimension around
existing points. That is not quite the same as generating new points that
belong to a small dimension manifold in the sample space.*

We acknowledge this limitation of our data augmentation process; we added discussion about an improved data augmentation process as future work in our Discussion section.

@@

*Section 2.2 is meant to be the definition of the search problem(s), but
that is really only contained in the paragraph from lines 218 to 223. In
any case, it is essential to put the problem(s) to be solved earlier, that
is, first, before any description of the solutions with ideas such as
clusters.  This movement of text will require a bit of text refactoring at
a minimum.  Also, the sentence at lines 221 to 223 should be expanded in
full detail into a separate paragraph.  Finally, one assumes that the
integer $k$ or the number $\rho$ is a parameter to the corresponding
problem and should be mentioned as such.*

We have refactored the methods section to have a better flow, and have defined several terms in their proper place.
We have also removed $\rho$-NN search from the main body of the paper in order to focus exclusively on $k$-NN search.
The supplement now contains a section on the improvements to $\rho$-NN search.

*There are no theorems in the manuscript, yet there are arguments for
quantities like the quality of the results or the time complexity that are
given without much precision.  It is better to give precise theorems or
propositions for each thing to be proved, with appropriate assumptions,
and to give precise proofs of same.*

We have expressed claimed time complexities as precise theorems with assumptions and provided proofs.

### 2025-01-15 sections/5-discussion.tex
updated todos and added data aug to discussion

>>>>

Additionally, we intend to improve the data augmentation process described in Section~\ref{sec:methods:synthetic-data} to better preserve the topological structure of the underlying dataset. 
In particular, we expect that favoring augmentation along the first principal components of the local manifold may allow for more realistic data augmentation.
